---
title: "FAANG Stock and Return Graph"
author: "Songju Kim"
date: '2020 7 8 '
output: slidy_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction of Project

FAANG (Facebook, Amazon, Apple, Neflix, Google) Stocks are so popular nowadays.

These IT giants' stock surged up for a long time.

This Shiny Web app shows these stocks' performance and additional technological analysis.


```{r, echo=FALSE}
# Define variable containing url
url <- "https://specials-images.forbesimg.com/imageserve/5da63b70db40260006202a39/960x0.jpg?fit=scale"
```

<center><img src="`r url`"> </center>

## Quantmod packages

To deal with financial data, you need to install quantmod packages.

```{r echo=TRUE}
library(quantmod)
```

These are frequently used functions of quantmod

- getSymbols()
- chartSeries()
- dailyReturn(),weeklyReturn(),monthlyReturn()...etc

## Layout of Shiny Web UI

Inputs

- selectInput    : contains FAANG stock symbol code
- dateRangeInput : represents date interval to get Symbols
- selectInput    : containts Return type for showing another chars
- actionButton   : request
- selectInput    : choices for chart type
- checkInputs and action button for technical analysis 

Outputs

- Basic chart( date, price)
- Return chart( time series, return)

## Reactive elements

- dataInput, dateInput\
  Select one stock symbol or change interval, \
  Output reflects these changes with actionButton Click
  
- taOptions\
  It draws added options.\
  
- returns\
  It transforms symbol prices into return rate based on \
  selected time interval
    
**With reactive elements, inputs are conneted to outputs dynamically.**